Croder \\ Bringing the Knowledge of the Crowds into the IDE

### 2013-05-02 paper/paper.tex
Format to SIGCHI standard.

\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\title{Croder \\ Bringing the Knowledge of the Crowds into the IDE}
\author{Semih Okur \and Mihai Codoban \and Caius Brindescu \and Kyungho Lee \and Shuo Yuan}

>>>>

\documentclass[]{sigchi}

% Arabic page numbers for submission. 
% Remove this line to eliminate page numbers for the camera ready copy
\pagenumbering{arabic}

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs

% llt: Define a global style for URLs, rather that the default one
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
\makeatother
\urlstyle{leo}

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}

% Make sure hyperref comes last of your loaded packages, 
% to give it a fighting chance of not being over-written, 
% since its job is to redefine many LaTeX commands.
\usepackage[pdftex]{hyperref}
\hypersetup{
pdftitle={SIGCHI Conference Proceedings Format},
pdfauthor={LaTeX},
pdfkeywords={SIGCHI, proceedings, archival format},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}

% create a shortcut to typeset table headings
\newcommand\tabhead[1]{\small\textbf{#1}}

\title{Croder \\ Bringing the Knowledge of the Crowds into the IDE}
\author{Semih Okur \and Mihai Codoban \and Caius Brindescu \and Kyungho Lee \and Shuo Yuan}
\numberofauthors{5}
\author{
  \alignauthor Semih Okur\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{okur2@illinois.edu}
  \alignauthor Mihai Codoban\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{codo@illinois.edu}
  \alignauthor Caius Brindescu\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{brind@illinois.edu}
   \alignauthor Kyungho Lee\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{klee141@illinois.edu}
  \alignauthor Shuo Yuan\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{syuan20@illinois.edu}
}
